\documentclass[a4paper]{book}
\usepackage[times,inconsolata,hyper]{Rd}
\usepackage{makeidx}
\usepackage[latin1]{inputenc} % @SET ENCODING@
% \usepackage{graphicx} % @USE GRAPHICX@
\makeindex{}
\begin{document}
\chapter*{}
\begin{center}
{\textbf{\huge Conformal: an R package to calculate prediction errors in the conformal prediction framework}}
\par\bigskip{\large \today}
\end{center}
\inputencoding{utf8}
\HeaderA{conformal}{conformal: an R package to calculate prediction errors in the conformal prediction framework}{conformal}
\aliasA{conformal-package}{conformal}{conformal.Rdash.package}
%
\begin{Description}\relax
conformal permits the calculation of prediction errors in the conformal prediction framework:
(i) p.values for classification, and
(ii) confidence intervals for regression.
\end{Description}
%
\begin{References}\relax
Isidro Cortes <isidrolauscher@gmail.com>.
conformal: an R package to calculate prediction errors in the conformal prediction framework

Norinder et al. J. Chem. Inf. Model., 2014, 54 (6), pp 1596-1603        
DOI: 10.1021/ci5001168       
\url{http://pubs.acs.org/doi/abs/10.1021/ci5001168}

\end{References}
\inputencoding{utf8}
\HeaderA{ConformalClassification}{Conformal Prediction For Classification}{ConformalClassification}
%
\begin{Description}\relax
R class to p.values for individual 
predictions according to the conformal prediction framework.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
ConformalClassification(...)
\end{verbatim}
\end{Usage}
%
\begin{Author}\relax
Isidro Cortes-Ciriano <isidrolauscher@gmail.com>
\end{Author}
%
\begin{References}\relax
Norinder et al. J. Chem. Inf. Model., 2014, 54 (6), pp 1596-1603
DOI: 10.1021/ci5001168
\url{http://pubs.acs.org/doi/abs/10.1021/ci5001168}
\end{References}
%
\begin{SeeAlso}\relax
\code{\LinkA{ConformalRegression}{ConformalRegression}}
\end{SeeAlso}
%
\begin{Examples}
\begin{ExampleCode}
# Optional for parallel training
#library(doMC)
#registerDoMC(cores=4)

data(LogS)

# convert data to categorical
LogSTrain[LogSTrain > -4] <- 1
LogSTrain[LogSTrain <= -4] <- 2
LogSTest[LogSTest > -4] <- 1
LogSTest[LogSTest <= -4] <- 2

LogSTrain <- factor(LogSTrain)
LogSTest <- factor(LogSTest)

algorithm <- "rf"

trControl <- trainControl(method = "cv",  number=5,savePredictions=TRUE, 
                          predict.all=TRUE,keep.forest=TRUE,norm.votes=TRUE)
set.seed(3)
model <- train(LogSDescsTrain, LogSTrain, algorithm,type="classification", 
               trControl=trControl)


# Instantiate the class and get the p.values
example <- ConformalClassification$new()
example$CalculateCVAlphas(model=model)
example$CalculatePValues(new.data=LogSDescsTest)
example$p.values$P.values
example$p.values$Significance_p.values

\end{ExampleCode}
\end{Examples}
